---
title: "Coal Efficiency"
author: "Andrew Mahurin"
date: "06/12/2015"
output: ioslides_presentation
---

## R Markdown


## Slide with Bullets


## Slide with R Code and Output

```{r}
energy = read.csv(file = "~/program/coal.csv")
energy
summary(energy)
```

Data is from http://www.eia.gov/electricity/annual/html/epa_08_01.html

## Slide with Plot

```{r, echo=FALSE}
#plot(xlim=c(2000,2013), ylim = c(5000,11000))
plot(energy$Year, energy$Coal,ylim = c(4000,11000), type = "l")
lines(energy$Year, energy$Natural.Gas)
```
Coal stays steady while the efficiency of Natural gas improves from year to year.

## How much electricity generation based on Natural gas is getting better from year to year

``` {r}
res= lm(energy$Natural.Gas~energy$Year)
summary(res)
```
## Plotting a straight line regression
``` {r}
plot(energy$Year, energy$Coal,ylim = c(4000,11000), type = "l")
lines(energy$Year, energy$Natural.Gas)

abline(res, col = "green")
```

## Calculating change based on logarithms
``` {r}
res2 = lm(log(energy$Natural.Gas)~energy$Year)
summary(res2)
```
## Plotting logarithmic values with regression line
``` {r}
#plot(energy$Year, log(energy$Coal))
#,ylim = c(4000,11000), type = "l")
plot(energy$Year, log(energy$Natural.Gas))
abline(res2, col = "green")
```
## Calculating based on differences in logs
``` {r}
time= 1:10
#diff(log(energy$Natural.Gas))
res3 = lm(diff(log(energy$Natural.Gas))~energy$Year[2:11])
summary(res3)
```

## Plotting differences in logs
``` {r}
plot(energy$Year[2:11], diff(log(energy$Natural.Gas)))
abline(res3)
```
The graph shows that energy usage to create electricity from natural gas decreased the most in the first year.
## How much has Natural Gas changed on the basis of percentage change
