---
title: "From a highpoint"
author: "Andrew Mahurin"
date: "05/27/2015"
output: ioslides_presentation
---

## Introduction

What is the expected price low point that happens in the next n days after stocks reach an all-time high?

Is any price drop to be expected to be lower than when the stock market is not at an all-time high?

What is the expected new price high point that happens subsequent to when stocks reach a new all-time high?

Is any price increase supposed to be lower than when when the stock market is not at an all-time high?


Is the low expected to be lower than 
in the next days after stocks reach an all-time high?
For more details on using R Markdown 
see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Details
- This project poses several challenges.
- The first is to load the data in.
- The second is to determine whether stocks at their maximum.
- Bullet 3

## Getting Data

```{r}
symbol = "SPY"
  URL <- paste("http://ichart.finance.yahoo.com/table.csv?s=",symbol, sep = "")
  dat <- read.csv(URL)
  dat$Date <- as.Date(dat$Date, "%Y-%m-%d")
  dat$Date <- rev(dat$Date)
  dat$Open <- rev(dat$Open)
  dat$High <- rev(dat$High)
  dat$Low <- rev(dat$Low)
  dat$Close <- rev(dat$Close)
  dat$Volume <- rev(dat$Volume)
  dat$Adj.Close <- rev(dat$Adj.Close)
```

## Finding the maximums
``` {r}
library("Rcpp")
cppFunction('
            NumericVector max1(NumericVector x){
  int n = x.size();
  NumericVector out(n);
//for(int i = 0; i < k; ++i) {
    out[0] = NA_REAL;
//  }
  for(int i = 1; i < n; ++i) {
    //out[i] = 
    if (x[i-1] >= x[i]) 
    {out[i] = x[i-1];}
    else if (x[i-1] < x[i]) 
    {out[i] = x[i];}
    else {
      out[i] = NA_REAL;
    }
  }
  return(out);
}

            ')

new1 = max1(dat$High)

```

## Another function

``` {r}
cppFunction('
            NumericVector rollingmax(NumericVector x){
  int n = x.size();
  NumericVector out(n);
  int lastmax = x[0];
//for(int i = 0; i < k; ++i) {
    out[0] = 1;
//  }
  for(int i = 1; i < n; ++i) {
    //out[i] = 
    if (x[i] > lastmax) 
    {out[i] = 1; lastmax = x[i];}
    else out[i] =0;
//if (x[i-1] < x[i]) 
//    {out[i] = x[i];}
//    else {
//      out[i] = NA_REAL;
//    }
  }
  return(out);
}

            ')

new2 = rollingmax(dat$High)
```

## Slide with Plot

```{r, echo=FALSE}
par(mfcol = c(2,1))
plot(dat$High)
plot(new1)
```

## Another plot

``` {r}
par(mfcol = c(2,1), col = new2)
plot(dat$High)
plot(new2)
```