---
title: "Interest Rates"
author: "Andrew Mahurin"
date: "05/21/2015"
output: html_document
---

## Introduction
How much does interest rates affect the growth of money over time?

How do small changes in the interest rate affect the growth of a portfolio?

How does the interest rate paid compare with the interest earned from investments?

If a state government has a low interest rate on debt that it borrows, and a high interest rate on investments that it invests, how much should it invest?

see <http://rmarkdown.rstudio.com>.



## Goals

- To make a graph showing the amount of interest that can be earned by a state government that invests in the stock market.
  * Actual returns will vary over time.
- To make a graph showing how much interest a state government would have to pay on debt incurred if it borrowed to invest in the stock market.
  *This may vary from state to state, depending on the situation.
- To demonstrate the benefits of investing in the stock market.
  *This won't be an unbiased presentation.


## Introducing variables

```{r}
#example
max_time = 100
initial_balance = 1
year <- 1:100
a = b = initial_balance
interest_rate1 = 10
interest_rate2 = 1.5
deposit = 1
r1 = interest_rate1 / 100
r2 = interest_rate2 / 100
for (time in 2:(max_time-1)){
a[time] = a[time-1] * (1+r1) + deposit
b[time] = b[time-1] * (1+ r2) + deposit
}
a[max_time] = a[max_time-1] * (1+r1)
b[max_time] = b[max_time-1] * (1+ r2)
```

## Summarizing variables
``` {r}
summary(cbind(a,b))
```

## Plotting variables

```{r, echo=FALSE}
#par(mfcol= c(2,1))
plot(year, a)
lines(year, b)
```

## Plotting the difference in account a and account b.
``` {r}
plot(1:100,a-b)
```

## Changing the variables

A 5% interest rate would be equivalent to what a county would be expected to pay in interest.

``` {r}
interest_rate2 = 5
r2 = .05
```
``` {r, echo=FALSE}
for (time in 2:(max_time-1)){
a[time] = a[time-1] * (1+r1) + deposit
b[time] = b[time-1] * (1+ r2) + deposit
}
a[max_time] = a[max_time-1] * (1+r1)
b[max_time] = b[max_time-1] * (1+ r2)
```
## Ploting the new results
```{r, echo=FALSE}
#par(mfcol= c(2,1))
plot(year, a)
lines(year, b)
```
